Recruiting Chapter

### 2021-06-11 text/tables_figures_june_2021.Rmd
add 1-mode plots

>>>>

## 1-mode plots

- `plot_1mode_pubu.pdf`
- `plot_1mode_privu.pdf`
- `plot_1mode_privc.pdf`
- `plot_1mode_u.pdf`, `plot_1mode_u_k5.pdf`
- `plot_1mode_all.pdf`, `plot_1mode_all_k5.pdf`, `plot_1mode_all_k6.pdf`

```{r}
include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))
include_graphics(file.path(figures_dir, 'plot_1mode_privu.pdf'))
include_graphics(file.path(figures_dir, 'plot_1mode_privc.pdf'))

include_graphics(file.path(figures_dir, 'plot_1mode_u.pdf'))
include_graphics(file.path(figures_dir, 'plot_1mode_u_k5.pdf'))

include_graphics(file.path(figures_dir, 'plot_1mode_all.pdf'))
include_graphics(file.path(figures_dir, 'plot_1mode_all_k5.pdf'))
include_graphics(file.path(figures_dir, 'plot_1mode_all_k6.pdf'))
```
